%-------------------------
% Resume in Latex
% Author : Hitarth Thanki
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{helvet}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\begin{center}
    \textbf{\Huge \scshape Hitarth Thanki} \\ \vspace{1pt}
    {\underline{letsconnect@hitarth.dev}} $|$ 
    {\underline{hitarth.dev}}  $|$
    {\underline{linkedin.com/in/hitarth-thanki}} $|$
    % \href{tel:+18325194502}{\underline{+1 (832) 519-4502}} $|$
    {\underline{github.com/brohudev}}  $|$
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Houston}{Houston, Texas, USA}
      {Bachelor of Science in Computer Science}{August 2022 -- May 2025}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Algorithms, Data Structures, Operating Systems, Database Systems, Software Design, Computer Architecture, Linear Algebra}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
     \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
         \textbf{Languages}{: Java(5 years), Python(3 years), C/C++(3 years), Javascript(2 years), R(1 year)} \\
         \textbf{Frameworks and Libraries}{(All 1 year): React, Node.js, Pygame, Tkinter, Material-UI, FastAPI} \\
         \textbf{Developer Tools}{: Git(3 years), Linux(2 years), Cloudflare CDN (1 year) , GitHub(3 years), Binwalk, GDB, Radare} \\
        }}
     \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{{Stellar Scholars}}}{Jan 2024}
          \resumeItemListStart
            \resumeItem{Built a web browser video game using \textbf{Javascript}, \textbf{React}, \textbf{Pixi.js}, and \textbf{Tailwind CSS} to teach kids about the planets and moons of the Solar System. Integrated \textbf{OpenAI API} to create a context-aware chatbot for educational guidance. Deployed on \textbf{Cloudflare Pages}.}
            \resumeItem{\textbf{Won 4 awards at TamuHack X (worth 500\$)}: Best Software Design (100\$), Best AI Application with Cloudflare (100\$), 4th place overall in Software track (250\$), and 3rd in the L3Harris Challenge (50\$).}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{{Dropawf}}}{Apr 2024}
          \resumeItemListStart
            \resumeItem{Developed a pet-themed post office app with \textbf{NodeJS}, \textbf{React}, and \textbf{MySQL} for tracking packages and managing addresses. Hosted frontend on \textbf{Cloudflare Pages} and backend on \textbf{Render} and \textbf{Azure}.}
            \resumeItem{Utilized \textbf{Git} for version control and continuously deployed to Cloudflare via \textbf{GitHub}.}
          \resumeItemListEnd

        \resumeProjectHeading
            {\textbf{CyberAuto and CyberDrone Conferences}}{Jul-Sept 2024}
            \resumeItemListStart
                \resumeItem{Gained real-world penetration testing experience on production drones and cars.}
                \resumeItem{Used tools like open5gs, Ghidra, binwalk, strace to \textbf{discover 3 Zero-Days Exploits} in a production drone system.}
            \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{Personal Portfolio}}{Aug. 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Developed \textbf{{Version 1}} as a single-page portfolio using \textbf{React}, showcasing a simple card layout.}
            \resumeItem{Developing Version 2 using Astro and Mard}
          \resumeItemListEnd
            
    \resumeSubHeadingListEnd




%-----------LEADERSHIP EXPERIENCE-----------
\section{Leadership Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Director of CodeRED}{Jan 2024 -- Present}
      {University of Houston}{Houston, Texas}
      \resumeItemListStart
        \resumeItem{Organized the largest hackathon in the Houston metropolitan area, with \textbf{450 participants}, \textbf{30\% female}, and \textbf{40\% from underrepresented groups}, overseeing all aspects of planning and implementation.}
        \resumeItem{\textbf{Managed a team of 20 leaders}, coordinating efforts in Design, Code, Marketing, and Sponsorship acquisition for CodeRED.}
        \resumeItem{Handled a budget of approximately \$40,000, optimizing resource allocation to maximize event impact.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Software Team Lead: USIP}{Jul 2023 -- Present}
      {University of Houston}{Houston, Texas}
      \resumeItemListStart
        \resumeItem{\textbf{Led a 6-member software development team} for the Undergraduate Student Instrumentation Project (USIP), managing coding tasks and team collaboration.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Historian: CougarCS}{Nov 2022 -- Dec 2023}
      {University of Houston}{Houston, Texas}
      \resumeItemListStart
        \resumeItem{\textbf{Captured and documented over 90 CougarCS events}, creating a visual and written record of key moments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%

%-------------------------------------------
\end{document}
